%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%    TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Yifu}{Wang}{ % Your name
\urlstyle{same}\url{https://www.linkedin.com/in/yifuwang} \\ % Your website, LinkedIn profile or other web address
\href{mailto:yifuwang92@gmail.com}{yifuwang92@gmail.com} | 626.226.6282 % Your contact information
}

%----------------------------------------------------------------------------------------
%    LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Carnegie Mellon UNIV}

\descript{MS in Computer Science}
\location{June 2016 | Pittsburgh, PA}

\sectionspace % Some whitespace after the section

\subsection{Dalian Univ of Tech}

\descript{BS in Computer Science}
\location{June 2014 | Dalian, China}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 

Github:// \href{https://github.com/wangyifu}{\bf https://github.com/wangyifu} \\
LinkedIn:// \href{https://www.linkedin.com/in/yifuwang}{\bf yifuwang} \
\
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Graduate}

Search Engine \\
Cloud Computing \\
Machine Learning \\
Adv. Data Structure and Algorithms \\
Convolutional Neural Networks for \\
Visual Recognition \\

{\footnotesize \textit{\textbf{(Teaching Assistant) }}} \\
Data Structures for Application Programmers \\
JAVA for Application Programmers

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Undergraduate}

Operating System \\
Compiler Techniques \\
Database Systems \\
Computer Network \\
Computer Architecture \\
Data Structure and Algorithms \\

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}
Python \textbullet{} Java \textbullet{} C++  \textbullet{} SQL \textbullet{} bash \textbullet{} Javascript
\sectionspace 
\subsection{Libraries \& Tools}
Pytorch \textbullet{} OpenCV \textbullet{} Xgboost \textbullet{} gtest \textbullet{} CMake
\sectionspace
\subsection{Everyday Using}
ElasticSearch \textbullet{} Docker \textbullet{} AWS \textbullet{} INotebook \textbullet{} Git

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%    RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Adobe Systems}
\descript{|~ Member of Technical Staff}
\location{July 2016 – Now | San Jose, CA}

\sectionspace

\descript{Content Analyzer Service}
\location{microservice, Docker, Flask, uwsgi, protobuf, json-schema, Elasticsearch}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Main developer of CAS, a deep learning as a service framework. 
\item The goal is to let researcher develop the model as a RESTful web service in a day.
\item Functionality including but not limited to: test, deploy, monitor, scale
\item Integrated popular deep learning frameworks: Caffe, Tensorflow, Pytorch
\item Allows models to use CPU, GPU or Elasticsearch by switching config
\item Supported analyzers written in C++, Python, and Java. 
\item Launched into the production environment with ~3k RPM in every region.
\end{tightitemize}

\sectionspace

\descript{Salability Analyzer}
\location{ElasticSearch, Xgboost, AWS, Docker}
\begin{tightitemize}
\item Fetched 1 million image data from AdobeStock as training dataset
\item Feature includes: image demand, image aesthetic value, visual similarity feature, tagging similarity feature
\item The target is defined as 6-month download normalized by clicks during the period
\item Got MAE(mean absolute error): 0.15, 10-DCG: 0.88
\item Deployed to Adobe Contributor Pipeline
\end{tightitemize}

\sectionspace % Some whitespace after the section

\descript{Car Brand Search}
\location{Pytorch, transfer learning}
\begin{tightitemize}
\item Validated the similarity model can be applied to specific categories
\item Trained a transfer learning model for car brand search
\item Fetched 500k image from AdobeStock with related category and title
\item Extracted feature vector from ResNet and VGGNet
\item Built a two-layer Fully Connected Network with dropout. Achieves 95\% accuracy
\end{tightitemize}

\sectionspace

%------------------------------------------------

\runsubsection{Quixey, Inc}
\descript{|~ Software Engineer Intern}
\location{May 2015 – August 2015 | Mountain View, CA}

\sectionspace

\descript{Chinese Query Tokenizer}
\location{Java, MongoDB, AWS, Hadoop}
\begin{tightitemize}
\item Implemented Chinese query tokenizer based on the dictionary and statistical language model. 
\item Developed RESTful web service using Jetty.
\item 40\% faster and 1.6\% DCG score gain compared with the previous tokenizer.
\item Integrated to Quixey app search and auto-suggestion.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{VMware, Inc}
\descript{|~ Full Stack Developer Intern}
\location{August 2013 – February 2014 | Beijing, China}

\sectionspace

\descript{QE dashboard}
\location{PHP, MySQL, Javascript}
\begin{tightitemize}
\item Developed QE dashboard based on LAMP stack for visualizing QE progress, updating QE result, and generating result chart in excel and PDF format.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%    SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}